Figure 2 - Overview heatmaps for IP-MS and ChIP

### 2024-07-08 ms_figure_2_overview-heatmaps.Rmd
remove unneeded packages

```{r load-packages, class.source="fold-show"}
suppressPackageStartupMessages({
    library(SingleCellExperiment)
    library(ggplot2)
    library(cowplot)
    library(dplyr)
    library(forcats)
    library(jsonlite)
    library(ComplexHeatmap)
    library(colorspace)
    library(circlize)
    library(scattermore)
    # library(ggrepel)
    # library(DT)
    # library(stringr)
    library(tidyr)
    # library(kableExtra)
    # library(patchwork)
})

>>>>

```{r load-packages, class.source="fold-show"}
suppressPackageStartupMessages({
    library(SingleCellExperiment)
    library(ggplot2)
    library(cowplot)
    library(dplyr)
    library(forcats)
    library(jsonlite)
    library(ComplexHeatmap)
    library(colorspace)
    library(circlize)
    library(scattermore)
    library(tidyr)
})
